### 2017-02-04 thesis/latex/thesis.tex
Thesis: Add method for estimating time in one/bothbound from today's meeting.

>>>>

\paragraph{Fitting rate constants to processivity and step times}
Rate constants can be fit to experimentally measurable values, such as velocity and the time dynein is bound to the microtubule (processivity time). We define the following values:

\newcommand\tbb{\left<t_{bb}\right>}
\newcommand\tob{\left<t_{ob}\right>}
\newcommand\tstep{\left<t_{step}\right>}
\newcommand\tproc{\left<t_{processivity}\right>}
\newcommand\kub{k_{ub}}
\newcommand\kb{k_{b}}
\newcommand\ko{k_{dis}}

\begin{itemize}
\item $\tbb$: Time in bothbound per step
\item $\tob$: Time in onebound per step
\item $\tstep$: Time of a single step. $\tstep=\tbb+\tob$.
\item $P_{bb}$: Probability of being bothbound per unit time. $P_{bb} = \frac{\tbb}{\tstep}$
\item $P_{ob}$: Probability of being onebound per unit time. $P_{ob} = \frac{\tob}{\tstep}$
\item $\kub$: Rate of unbinding per unit time while in bothbound. $\kub = \tbb^{-1}$
\item $\kb$: Rate of binding per unit time while in onebound. $\kb = \tob^{-1}$
\item $\ko$: Rate of unbinding per unit time while in onebound. $\ko = P_{ob}\kub$
\item $\tproc$: Time bound to microtubule before dissociation. step length / velocity $= \ko^{-1}$
\end{itemize}

$\tbb$ and $\tob$ can thus be defined in terms of observables $\tstep$ and $\tproc$:

\begin{align*}
  \ko &= P_{ob}\kub = \frac{\tob}{\tstep\tbb}\\
  &= \frac{\tstep-\tbb}{\tstep\tbb}\\
  &= \frac{\tstep-\tbb}{\tstep\tbb}\\
  \tbb &= \frac{\tstep\tbb}{\tstep-\tbb}\\
  \tob &= \tstep-\tbb\\
  &= \tstep - \frac{\tstep\tbb}{\tstep-\tbb}\\
  &= \frac{\left(\tstep-\tbb\right)\tstep\tbb}{\tstep-\tbb}\\
  &= \frac{\tstep\left(\tstep-\tbb\right) - \tstep\tbb}{\tstep-\tbb}\\
  &= \frac{\tstep^2}{\tstep-\tbb}\\
\end{align*}

Thus, by the above equations and using data from (put right paper here), values for $\tbb$ and $\tob$ can be found:

\begin{figure}[h]
  \centering
  \begin{tabular}{| c | c | c | c | c | c |}
    \hline
    Velocity & $\left<L_{step}\right>$ & $\tstep$ & $\tproc$ & $\tbb$ & $\tob$ \\ \hline
    100nm/s & 8nm & 0.08 & 3s & 0.08 & 0.002 \\ \hline
  \end{tabular}
  \caption{Table calculating estimates for $\tbb$ and $\tob$.}
  \label{table:parameter-table}
\end{figure}

Todo: get real values for above velocity/steplenght/steptime/processivity based on \textit{in vivo} ATp concentration.\\
